Modern embedded systems feature multiple general purpose cores, which improve application performance by executing its independent threads simultaneously. 
As more processing cores are integrated in a system, the chip power consumption increases, reducing the energy autonomy.
Nowadays, Operating System, even Embedded Operating System, implements different managers, named \textit{governors} in Linux, only based on the cores' workload criterion and acting on cores' clock frequency through Dynamic Voltage-Frequency Scaling (DVFS). 
Although these governors can be efficient for not performance constrained usages, they cannot provide enough efficiency for application that require specific performance guarantee, especially for throughput constrained streaming applications.\\
For this reason, more and more people intent to design some managers which would be able to guarantee the performance while minimizing power consumption. 
The solution which seems to be standing out of the crowd is to the Reinforcement Learning. \cite{das2015hardware}\cite{molnos2016investigation}\cite{tesauro2007managing} This area of machine learning science seems to be particularly adapted for this application.\\

In this context, the LIALP laboratory, had experimented this technique on a prototyped platform and had satisfactory results. Then, their motivation was to create a software infrastructure to demonstrate this technique in a standard software stack running on an out-of-the-shelf platform. The idea to apply the most advanced research technique to an industrial aim is the core business CEA. And this was my mission during my three month internship inside CEA Grenoble.\\

This internship report is organised in four main parts. First of all, the context of the internship will be presented. Then, the second part explains the problem and the objectives to lead the internship to a success. The third part is related to my contribution, exposed from general view to a more detailed presentation. The last main section deals with the results of my work. This report will be concluded and opening will be suggested.\\